Determining the Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm

### 2023-11-10 paper/SST/3-response_reviewer1.tex

We are sorry for our negligence of the grammatical and spelling errors, and have carefully checked the manuscript and corrected them.

\end{revresponse}

% Comment 2
\begin{revcomment}
  Since authors stated that there is no existing works on the MAC determination of RBSs that they could compare their solution with. So how the authors validate their works and their results.
\end{revcomment}
\begin{revresponse}

% We infer that the reviewer may desire to convey: since the authors stated that there are no existing works on the MAC determination of RBSs that they could compare their solution with, it is important to meticulously and comprehensively elucidate how the authors validate their works and the results.

To address the concern raised by the reviewer, we have incorporated a comprehensive discussion in the Case study section, specifically titled "Result validation". 
In this part, we thoroughly examine the correctness of the results obtained through the proposed greedy algorithm from two distinct perspectives: circuit analysis and validation against the brute-force algorithm. 
Additionally, we have included a comparison between the proposed greedy algorithm and two heuristic algorithms, namely simulated annealing and genetic algorithm, in the revised manuscript. 
There is a reference (No. 35 in the manuscript) claiming that the path selection problem under consideration may be NP-hard.
Therefore, it is reasonable to compare the performance of the proposed greedy algorithm with these heuristic approaches, which are commonly employed to tackle NP-hard problems.
Remarkably, our results demonstrate that the proposed greedy algorithm consistently achieves the same or superior outcomes compared to the heuristic algorithms.

### 2023-11-15 paper/SST/3-main.tex
Add revised manuscript and response to reviewer comments
fix and modify cover letter and response
按 Q 的意见修改
polished 3-main from professional organization

% =====2-review outline======
% 1. intro 文献综述部分：重写、补充，引用c8的文献；对RBS性能的分析
%   1.1 任务分配：如果从电流分配的角度考虑，这是一个 NP-hard 问题，求解这类问题的开销一般很大，通过针对性地改进传统算法来解决计算开销，例如 Mollajafari 提出了 a meta-heuristic method named Graph-Oriented Simulated Annealing (GOSA) )(结合 gammoudiEnergyEfficientSchedulingRealTime2020 这篇可重构任务调度的文章)
%   1.2 对RBS性能的分析
%   1.3 多说一点启发式算法
% 2. case study 增加实验 模拟退火、遗传算法；增加b结构的2，6数量的电池
%   2.1 structures and details
%       2.1.1 4-battery 不同结构（3个tab：our method；1个图）
%       2.1.2 2/4/6-battery 结构c
%       2.1.3 4-battery 不同结构 isolated battery
%       2.1.4 四种计算方法
%   2.2 result: 删去table4和前面一段话；添加文字，描述figure7；使用子图子表格
%       2.1.1 c结构的计算细节：1组fig（有向图、SP、最终结果）
%       2.1.2 4-battery 不同结构的计算结果：1组tab（各结构计算结果）、2组fig（各结构MAC正确闭合方案+算法迭代过程中的MAC折线图）
%       2.1.3 2/4/6-battery 结构c（1,2,3 *2）的计算结果：1组tab（各结构计算结果）、2组fig（各结构MAC正确闭合方案+算法迭代过程中的MAC折线图）
%       2.1.4 4-battery c 不同 isolated battery 的计算结果：1组fig（不同电池数的开关闭合方案）
%   2.3 discussion:
%       2.3.1 结果正确性和准确性：a. 电路分析；b. 与 force-brute 结果的验证
%       2.3.2 算法的有效性和优劣：a. 复杂度；b. 与 SA、GA 的比较(启发式算法仅找到局部最优；收敛时间)；c. 本算法的优劣和原因
%       2.3.3 this work 的意义和应用：a. 说明 eta 的意义、应用方法；b. 结合 isolated battery 说明应用场景
% 3. conclusion 相关内容修改
% 4. abstract 相关内容修改

% ! NOTE
% [DONE]
% 1. red mark -> blue mark
% 2. check ref
% 3. rewrite the last two paragraphs of the introduction if time permits

@@

%%%%%% Title %%%%%%
% Full titles can be a maximum of 100 characters, including spaces. 
% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
% \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}

@@

%%%%%% Abstract %%%%%%
\begin{abstract}
Reconfigurable battery systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure that can be adapted to different battery charging and discharging strategies.
During RBS operation, a critical system parameter known as the maximum allowable current (MAC) become pivotal. This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, thereby ensuring its safety and reliability.
This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
By introducing the shortest path (SP) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithm) into the combination of the shortest paths.
This significantly enhances the efficiency with which the MAC is determined.
The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
The proposed method is validated on two published RBS structures and one with a more complex structure.
The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable batteries, even in scenarios with random isolated batteries.
\end{abstract}

@@

Battery energy storage systems (BESSs) are widely utilized in various applications \cite{yangBatteryEnergyStorage2018}, such as wind power plants \cite{desiqueiraControlStrategySmooth2021} and space power systems \cite{schwanbeckInternationalSpaceStation2019,zhangDevelopmentProspectChinese2021}, for the purpose of storing and releasing high-quality electrical energy \cite{choCommercialResearchBattery2015}.
Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required storage capacity.
However, conventional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
Furthermore, if the worst battery fails during operation, it is highly likely to accelerate the degradation of the other batteries, resulting in reliability and safety issues at the system level \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
These challenges have become major technical obstacles in many engineering projects that demand high reliability, such as the development of next-generation space vehicles \cite{pomboHybridPowerSystem2021}.
Reconfigurable battery systems (RBSs), which can dynamically switch between different circuit topologies as needed, are expected to address these issues \cite{hanNextGenerationBatteryManagement2020a}.
In a typical RBS, additional switches are introduced between the batteries to form a reconfigurable network, where the circuit's topology can be altered by opening or closing the switches.
By opening the switches adjacent to the unhealthy batteries, they can be isolated from the system, ensuring that the system remains in a reliable operational state \cite{ci2016reconfigurable}.
Furthermore, the RBS can be reconfigured to adapt to different charging and discharging strategies, thereby enhancing the system's efficiency and prolonging the battery's lifespan \cite{bouchhima2018lifetime}.
These advantages make RBSs a promising alternative to traditional BESSs.

The early research on RBSs mainly focused on the topological design of the structure, incorporating different levels of flexibility and reconfigurability to meet application requirements.
For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to accommodate the constantly changing voltage requirements during electric vehicle charging.
The structure proposed by Visairo et al. \cite{visairoReconfigurableBatteryPack2008} alters the system's output voltage based on the load conditions, thereby reducing power loss in the voltage regulator during the power supply process and enhancing energy efficiency. 
Also, to enhance the energy efficiency of the system, Lawson et al. \cite{lawsonSoftwareConfigurableBattery2012} and He et al. \cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure. 
However, these complex structures between batteries and switches provide flexibility to RBSs while also posing challenges in hardware design. 
During the reconfiguration process, current deviation and fluctuation may occur. Specifically, when the system switches from series to parallel connection, circulating current between parallel cells can be triggered due to voltage imbalance \cite{hanAnalysisEstimationMaximum2020}. Failure to fully consider this issue during the design of RBSs can result in damage to the batteries, switches, and wires. 
For example, Engelhardt et al. \cite{engelhardtDoubleStringBatterySystem2021} applied RBS to a fast-charging scenario with adaptive cell switching, which can balance cell states while adhering to voltage requests. However, the switching of batteries leads to intolerable current variations. 
To address this problem, Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration. This analytical expression aids in the selection of switches and supports the hardware design of RBSs.

Recently, there has been increasing attention given to the estimation and control of the system state of RBSs, and several approaches have been proposed to optimize the performance of the system. 
State estimation, which is an essential technology in traditional battery management systems, serves as the foundation for system control and holds great potential in the context of RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
Couto et al. \cite{coutoPartitionbasedUnscentedKalman2018a} introduced a partition-based unscented Kalman filter to estimate the state of a large-scale RBS, utilizing an enhanced reduced-order electrochemical model. 
Kersten et al. \cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine battery impedance, thereby obtaining information about the state of health and power capability. 
Schmid et al. \cite{schmidActiveModelBasedFault2021a} further leveraged the reconfigurable nature of the system to actively diagnose faults, employing an algorithm that changes the system structure to enhance fault isolability. 
Another active research topic is the development of effective control strategies for RBSs to achieve optimal performance, including improved stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}.
Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the time required for battery charge equalization.
Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a scheme for maximizing capacity utilization based on a path planning algorithm, aiming to enhance battery consistency within the system.
To break through the bottleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory. 
They conducted a comprehensive analysis of all paths between the cathode and anode of each battery in the RBS, identifying paths that only consist of switches as short-circuit paths for pre-checking before system reconfiguration. 
Furthermore, Artificial Intelligence also appears in the RBS management \cite{liuLongLifetimeBattery2022a}.
The effectiveness of deep reinforcement learning method has been validated in real-world RBSs \cite{yangAdaptiveControlFramework2022}.

The maximum allowable current (MAC), which is defined as the maximum current allowed within the constraints of the battery cell, is a crucial indicator of RBSs that needs to be evaluated during the design and control of the system. 
The MAC assists designers in assessing whether the RBS meets the requirements for output current and contributes to the development of appropriate and safe management strategies for the battery management system. 
Unfortunately, there have been few studies proposed to directly determine the MAC of RBSs, primarily due to the complexity arising from reconfiguration. 
In the field of computer science, there is a similar problem of scheduling tasks on dynamically reconfigurable hardware with limited resources and task interdependencies, which is analogous to the determination of MAC. 
A corresponding method has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}. 
However, dealing with the structural characteristics and circuit equations of RBSs is challenging for this method.  
From the perspective of RBS structure analysis, the MAC problem can be transformed into finding the maximum output current among all possible reconfigurations of the RBS. 
However, this may be an NP-hard problem \cite{pinterReviewControlAlgorithms2021a}. 
Common methods such as brute-force algorithms, simulated annealing (SA) algorithms, and genetic algorithms (GA) have the drawbacks of inefficiency, time consumption, and inability to guarantee the globally optimal solution.

To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
In this method, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
This algorithm transforms the inefficiently searching reconfigurations into the proactively combining of the shortest paths of batteries.
Furthermore, an improved directed graph model is introduced to analyze the current of the RBS, taking into account factors such as voltage, internal resistance, MAC of the battery, and external load. 
The main contributions of this study can be summarized as follows:
\begin{itemize}
  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
  \item A greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
  \item An improved directed graph model is introduced to provide a specific method for calculating the MAC of a given structure.
\end{itemize}

The remainder of this paper is organized as follows: 
Section II presents the framework and details of the proposed directed graph model and greedy algorithm. 
Section III examines a case study that applies the proposed method to determine the MACs of two published RBS structures and one with a more complex structure. 
The calculation results, the computational complexity of the algorithm, and scenarios such as battery random isolation are also discussed. 
Finally, the concluding remarks are presented in Section IV.

@@

The central principle of this method is to connect the batteries in an RBS in parallel to the extent possible, thereby maximizing the output current of the RBS.
To achieve this universally and automatically, the overall process is divided into the four steps shown in Fig. \ref{fig:main}.
First, a directed graph model is established for subsequent computations. The model not only contains the connected relationships between batteries and switches but also retains the performance parameters of the batteries.
Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
The shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{main.png}
    \end{subfigure}
    \caption{ 
        Diagram of this method, which contains four main steps.
    }
    \label{fig:main}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-he.png}
        \caption{}
        \label{fig:direct-graph-he}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-xu.png}
        \caption{}
        \label{fig:direct-graph-xu}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-my.png}
        \caption{}
        \label{fig:direct-graph-my}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{battery_simple.png}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    \caption{ 
        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) the improved model in this paper.
        (d) The equivalent circuit of a battery in this method.
    }
\end{figure}

He et al. \cite{heExploringAdaptiveReconfiguration2013} proposed an abstracted directed graph model for an RBS, where the nodes represent the batteries, the edges represent the configuration flexibility, and the weight of each vertex corresponds to the battery voltage (Fig. \ref{fig:direct-graph-he}). 
The model captures all potential system configurations and offers a direct metric for configuration flexibility, but it does not specify the physical implementation of the connectivity between batteries, meaning that one graph might correspond to multiple RBS structures.
We previously proposed a directed graph model that differs completely from He's model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig. \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model. 
This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider  the voltage, internal resistance, and MAC of the battery. 
To address this issue, we improve our previous model by adding electromotive force and resistance attributes on the edges based on its equivalent circuits.
The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analyzes.
Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
The following  provides a detailed explanation of the method for equating components in RBSs and constructing the directed graph model.

To use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
For instance, as shown in Fig. \ref{fig:battery_simple}, the battery in the RBS is represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor $C$, known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
Therefore,  battery $B_i$ in the RBS can be simplified as a series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
Furthermore, the state of switch $S_j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
When the switch is closed, the circuit can be regarded as a resistor with a very small resistance $r_{j}$.
Finally, the external load is considered as a resistor with resistance $R_o$.

For a given RBS structure, its directed graph model $G(V,E)$ is constructed as follows:
\begin{enumerate}
    \item Nodes:
        The nodes in the directed graph correspond to the connection points of components in the actual RBS. 
        Assuming there are a total of $N$ nodes in the RBS, for the sake of convenience, the anode of the RBS is denoted as $v_1$ and the cathode as $v_N$.
    \item Edges:
        The edges in the directed graph correspond to the batteries, switches, and external electrical loads in the actual RBS.
        Therefore, there are three types of directed edges. 
        For battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode because the battery in operation only allows current to flow in one direction.
        For switch $S_j$, since it is allowed to work under bidirectional currents, it is represented by a pair of directed edges with two-way directions. 
        Regarding the external electronic load, because it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$  represents it. 
        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
    \item Attributes of edges:
        Each edge is assigned two attributes, voltage difference and resistance, based on the equivalent method mentioned above.
        The values for  battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
\end{enumerate}

@@

For a given RBS, determining its MAC involves maximizing the RBS output current while ensuring that all battery currents do not exceed the batteries' MAC. 
This subsection establishes the constraints and objective function to determine the RBS's MAC through circuit analysis based on the directed graph model provided in the previous section.

>>>>

@@

%%%%%% Title %%%%%%
% Full titles can be a maximum of 100 characters, including spaces. 
% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
% \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
\title{Determining the Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}

@@

%%%%%% Abstract %%%%%%
\begin{abstract}
Reconfigurable battery systems (RBSs) provide a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structures that can be adapted to different battery charging and discharging strategies.
A critical system parameter known as the maximum allowable current (MAC) is pivotal to RBS operation. This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, ensuring its safety and reliability.
In this paper, a method is proposed for calculating the MAC of an arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
Using the shortest path (SP) of the battery, the greedy algorithm transforms the exhaustion of the switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithms) in the combination of the shortest paths.
This significantly enhances the efficiency with which the MAC is determined.
The directed graph model, based on an equivalent circuit, provides a specific method for calculating the MAC of a given structure.
The proposed method is validated using two previously published RBS structures and an additional one with a more complex structure.
The results are the same as those from the brute-force algorithm, but the proposed method significantly improves the computational efficiency, being theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches.
Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable batteries, even in scenarios with random isolated batteries.
\end{abstract}

@@

Battery energy storage systems (BESSs) are widely utilized in various applications \cite{yangBatteryEnergyStorage2018}, such as wind power plants \cite{desiqueiraControlStrategySmooth2021} and space power systems \cite{schwanbeckInternationalSpaceStation2019,zhangDevelopmentProspectChinese2021}, for the purpose of storing and releasing high-quality electrical energy \cite{choCommercialResearchBattery2015}.
Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required storage capacity.
However, conventional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst batteries due to the so-called cask effect.
Furthermore, if the worst battery fails during operation, it is highly likely to accelerate the degradation of the other batteries, resulting in reliability and safety issues at the system level \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
These challenges have become major technical obstacles in many engineering projects that demand high reliability, such as the development of next-generation space vehicles \cite{pomboHybridPowerSystem2021}.
Reconfigurable battery systems (RBSs), which can dynamically switch between different circuit topologies as needed, are expected to be able to address these issues \cite{hanNextGenerationBatteryManagement2020a}.
In a typical RBS, additional switches are introduced between the batteries to form a reconfigurable network, where the circuit's topology can be altered by opening or closing the switches.
By opening the switches adjacent to the unhealthy batteries, they can be isolated from the system, ensuring that the system remains in a reliable operational state \cite{ci2016reconfigurable}.
Furthermore, an RBS can be reconfigured to adapt to different charging and discharging strategies, thereby enhancing the system's efficiency and prolonging the battery's lifespan \cite{bouchhima2018lifetime}.
These advantages make RBSs a promising alternative to traditional BESSs.

The early research on RBSs mainly focused on the topological design of their structures, incorporating different levels of flexibility and reconfigurability to meet application requirements.
For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
Jan et al. \cite{9209774,engelhardt2021double} designed structures that reconfigure circuits with variant batteries in series to accommodate the constantly changing voltage requirements during electric vehicle charging.
A structure proposed by Visairo and Kumar \cite{visairoReconfigurableBatteryPack2008} alters the system's output voltage based on the load conditions, thereby reducing power loss in the voltage regulator during the power supply process and enhancing energy efficiency. 
Lawson \cite{lawsonSoftwareConfigurableBattery2012} and He et al. \cite{he2014reconfiguration} also focused on enhancing energy efficiency, and proposed simplified structures that have fewer switches than the design of Visairo and Kumar.
Kim et al. \cite{kim2009dynamic} improved the ability of an RBS structure to recover from battery failures by introducing multiple ports. 
%<*reviewer2-comment1>
These complex structures between batteries and switches provide flexibility to RBSs but also pose challenges in hardware design. 
During the reconfiguration process, current deviation and fluctuation may occur. Specifically, when the system switches from series to parallel connection, a circulating current between parallel cells can be triggered due to a voltage imbalance \cite{hanAnalysisEstimationMaximum2020}. Failure to fully consider this issue during the design of RBSs can result in damage to the batteries, switches, and wires. 
For example, Engelhardt et al. \cite{engelhardtDoubleStringBatterySystem2021} applied an RBS to a fast-charging scenario with adaptive cell switching to balance cell states while adhering to voltage requests. However, the switching of batteries leads to intolerable current variations. 
To address this problem, Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration. This analytical expression aids in the selection of switches and supports general hardware design.

Recently, increasing attention has been paid to the estimation and control of RBS system states, and several approaches have been proposed to optimize the performance of these systems. 
State estimation, which is an essential technology in traditional battery management systems, serves as the foundation for system control and holds great potential in the context of RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
Couto et al. \cite{coutoPartitionbasedUnscentedKalman2018a} introduced a partition-based unscented Kalman filter to estimate the state of a large-scale RBS, utilizing an enhanced reduced-order electrochemical model. 
Kersten et al. \cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine the battery impedance, thereby obtaining information about the state of health and power capability of the RBS. 
Schmid et al. \cite{schmidActiveModelBasedFault2021a} further leveraged the reconfigurable nature of the system to actively diagnose faults, employing an algorithm that changes the system structure to enhance the fault isolability. 
Another active research area is the development of effective control strategies for RBSs to achieve optimal performance, including improved stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}.
Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the time required for battery charge equalization.
Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a scheme for maximizing capacity utilization based on a path planning algorithm, aiming to enhance the battery consistency within the system.
To break through the bottleneck of the potential short-circuit paths increasing exponentially with the RBS scale, Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory. 
They conducted a comprehensive analysis of all paths between the cathode and anode of each battery in the RBS, identifying paths that consist only of switches as short-circuit paths for pre-checking before system reconfiguration. 
Artificial intelligence has also appeared in RBS management \cite{liuLongLifetimeBattery2022a}.
The effectiveness of the deep reinforcement learning method has been validated in real-world RBSs \cite{yangAdaptiveControlFramework2022}.
%</reviewer2-comment1>

The maximum allowable current (MAC), which is defined as the maximum current allowed within the constraints of a battery cell, is a crucial indicator of RBSs that need to be evaluated during the design and control of the system. 
The MAC assists designers in assessing whether the RBS meets output current requirements and contributes to the development of appropriate and safe strategies for the battery management system. 
%<*reviewer1-comment3>
However, few studies have directly determined the MACs of RBSs, primarily due to the complexity arising from reconfiguration. 
In the field of computer science, there is a similar problem with scheduling tasks on dynamically reconfigurable hardware with limited resources and task interdependencies. This problem is analogous to the determination of the MAC and a corresponding solution has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}. 
However, dealing with the structural characteristics and circuit equations of RBSs is challenging for this method. 
%</reviewer1-comment3>
From the perspective of RBS structure analysis, the MAC problem can be transformed into a problem of finding the maximum output current among all possible reconfigurations of the RBS. 
However, this may be an NP-hard problem \cite{pinterReviewControlAlgorithms2021a}. 
Common methods such as brute-force algorithms, simulated annealing (SA) algorithms, and genetic algorithms (GA) have the drawbacks of inefficiency, excessive time consumption, and an inability to guarantee the globally optimal solution.

To solve this issue, this paper proposes an efficient method to evaluate the MACs of RBSs. 
In this method, a greedy algorithm is designed to efficiently search the possible circuit topologies of RBSs.
This algorithm transforms the inefficient search for reconfigurations into a proactive combining of the shortest paths of the batteries.
Furthermore, an improved directed graph model is introduced to analyze the current of the RBS, taking into account factors such as the voltage, internal resistance, MAC of the battery, and external load. 
The main contributions of this study can be summarized as follows:
\begin{itemize}
  \item An efficient method is proposed to determine the MACs of RBSs with arbitrary structures, including scenarios with isolated batteries.
  \item A greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
  \item An improved directed graph model is introduced to provide a specific method for calculating the MAC of a given structure.
\end{itemize}

The remainder of this paper is organized as follows: 
Section II presents the framework and details of the proposed directed graph model and the greedy algorithm. 
Section III applies the proposed method to determine the MACs of two published RBS structures and a new one with a more complex structure. 
The calculation results, the computational complexity of the algorithm, and scenarios such as battery random isolation are also discussed. 
Finally, the concluding remarks are presented in Section IV.

@@

The central principle of the proposed method is to connect the batteries in an RBS in parallel to the maximum possible extent, thereby maximizing the output current.
To achieve this universally and automatically, the overall process is divided into the four steps shown in Fig. \ref{fig:main}.
First, a directed graph model is established for the subsequent computations. The model not only contains the connected relationships between batteries and switches but also retains the performance parameters of the batteries.
Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
The shortest paths (SPs, where additional batteries and switches on the path are penalized for distance) of the batteries are then obtained using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{main.png}
    \end{subfigure}
    \caption{ 
        A diagram of the proposed method, which contains four main steps.
    }
    \label{fig:main}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-he.png}
        \caption{}
        \label{fig:direct-graph-he}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-xu.png}
        \caption{}
        \label{fig:direct-graph-xu}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-my.png}
        \caption{}
        \label{fig:direct-graph-my}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{battery_simple.png}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    \caption{ 
        The directed graph models used in (a) the work of He et al. \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) the improved model in this paper.
        (d) The equivalent circuit of a battery in this method.
    }
\end{figure}

He et al. \cite{heExploringAdaptiveReconfiguration2013} proposed an abstracted directed graph model for an RBS, where the nodes represent the batteries, the edges represent the configuration flexibility, and the weight of each vertex corresponds to the battery voltage (Fig. \ref{fig:direct-graph-he}). 
The model captures all potential system configurations and offers a direct metric for configuration flexibility, but it does not specify the physical implementation of the connectivity between batteries, meaning that one graph might correspond to multiple RBS structures.
We previously proposed a directed graph model that differs significantly from He et al.'s model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig. \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between an RBS structure and its directed graph model. 
This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider the voltage, internal resistance, or MAC of the battery. 
To address this issue, we improve our previous model by adding electromotive force and resistance attributes on the edges based on the corresponding equivalent circuits.
The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analysis.
Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
The following provides a detailed explanation of the method used for equating components in RBSs and constructing the directed graph model.

To use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
For instance, as shown in Fig. \ref{fig:battery_simple}, the battery in the RBS is represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor $C$, in what is known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
Therefore, battery $B_i$ in the RBS can be simplified as a series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
Furthermore, the state of the switch $S_j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
When the switch is closed, the circuit can be regarded as a resistor with a very small resistance $r_{j}$.
Finally, the external load is considered as a resistor with resistance $R_o$.

For a given RBS structure, its directed graph model $G(V,E)$ is constructed as follows:
\begin{enumerate}
    \item Nodes:
        The nodes in the directed graph correspond to the connection points of components in the actual RBS. 
        Assuming there are a total of $N$ nodes in the RBS, for the sake of convenience, the anode of the RBS is denoted as $v_1$ and the cathode as $v_N$.
    \item Edges:
        The edges in the directed graph correspond to the batteries, switches, and external electrical loads in the actual RBS.
        Therefore, there are three types of directed edges. 
        For battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode because the battery in operation only allows current to flow in one direction.
        For switch $S_j$, since it is allowed to work under bidirectional currents, it is represented by a pair of directed edges with two-way directions. 
        For the external electrical load, because it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$ is used to represent it. 
        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the number of directed edges is $N_b+2N_s+1$, where 1 represents the external electrical load.
    \item Attributes of edges:
        Each edge is assigned two attributes, a voltage difference and a resistance, based on the equivalent method mentioned above.
        The values for battery $B_i$, switch $S_j$, and the external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
\end{enumerate}

@@

For a given RBS, determining the MAC involves maximizing the RBS output current while ensuring that all battery currents do not exceed the batteries' MAC. 
This subsection establishes the constraints and objective function used to determine the MAC through circuit analysis based on the directed graph model provided in the previous section.
